Technical Report

### 2024-02-17 Reports/tech_report1.tex

>>>>

This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new hyperplane constraints.

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py|. And the partial output file name is \verb*|Gamma_5x100_normal_layer5_seek_openrelu.txt|.  It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 021600302024

	\item\emph{Open $\ReLU$ number:} Open 17,20,23,26,29 ReLU nodes for each node.
